%------------------------
% Resume Template (Modified for Chinmayi N)
% Header with icons style + Refined Experience/Education formatting
%------------------------

\documentclass[a4paper,10pt]{article}
\setlength{\footskip}{3.6pt}



\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\evensidemargin}{-0.45in}
\addtolength{\textwidth}{0.9in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\vspace{-6pt}\scshape\raggedright\large}{}{0em}{}[\titlerule\vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEduheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {#3} & {#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%
\begin{document}
%----------HEADING----------
\begin{center}
    {\Huge \scshape Chinmayi N} \\ \vspace{2pt}
    Bangalore, India \\ \vspace{2pt}
    \scriptsize
    \faPhone\ +91-XXXXXXXXXX ~
    \faEnvelope\ \href{mailto:email@example.com}{email@example.com} ~
    \faLinkedin\ \href{https://linkedin.com/in/username}{linkedin.com/in/username} ~
    \faGithub\ \href{https://github.com/username}{github.com/username}
    \vspace{-8pt}
\end{center}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bharat Electronics Limited (BEL)}{Aug 2025 -- Present}
      {Software Trainee}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Built React.js, Core Java, and PostgreSQL modules.}
        \resumeItem{Implemented session management, captcha-secured login, and load testing for 30k+ users.}
      \resumeItemListEnd

    \resumeSubheading
      {National Skill Development Corporation (NSDC)}{Jan 2025 -- Apr 2025}
      {AI Business Intelligence Analyst}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Applied AI/ML for data analysis with Python, Excel, and Power BI.}
        \resumeItem{Designed dashboards and insights for decision making.}
      \resumeItemListEnd

    \resumeSubheading
      {TechByHeart}{Aug 2024 -- Sep 2024}
      {Cyber Security Intern}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Worked with Kali Linux, practiced vulnerability assessment and penetration testing.}
        \resumeItem{Studied OSI/TCP-IP models and web application vulnerabilities.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{DevOps Integrated Weather Dashboard:} Built real-time weather app using HTML/CSS/JS and OpenWeatherMap API, CI/CD with Jenkins, GitHub Pages, monitoring with Grafana Cloud and Uptime Robot.}
    \resumeItem{\textbf{Air Quality Index Prediction:} Developed ML models (SVR, Decision Tree, Lasso) and deployed via Flask for real-time AQI predictions and visualization.}
    \resumeItem{\textbf{AI-Powered Sketch-to-Image Converter:} Created pipeline with CNN, GPT-2, ControlNet, and Stable Diffusion for sketch classification, prompt generation, and image synthesis.}
    \resumeItem{\textbf{IoT Smart Greenhouse:} Designed Arduino-based greenhouse with sensor monitoring, automated device control, and real-time cloud alerts.}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeItem{Languages: Python, Java, C, HTML, CSS, JavaScript}
    \resumeItem{Frameworks: React, Node.js, Flask, OpenCV}
    \resumeItem{Databases: MySQL, PostgreSQL}
    \resumeItem{DevOps/Tools: Git, GitHub, Jenkins, Linux, VS Code, Arduino IDE}
  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements \& Certifications}
  \resumeSubHeadingListStart
    \resumeItem{IBM: Finalist - Skills \& 1M1B EcoEquify Hackathon}
    \resumeItem{NPTEL: Problem Solving in C, Programming in Java, Joy of Computing with Python}
    \resumeItem{Coursera: Google AI Essentials}
    \resumeItem{Red Hat: Red Hat System Administration}
    \resumeItem{Other: Getting Started with Threat Intelligence and Hunting}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEduheading
      {B.N.M Institute of Technology, Bangalore}{Dec 2022 -- Present}
      {Bachelor of Engineering in Computer Science \& Engineering - CGPA: 9.5}{}

    \resumeEduheading
      {Vidyanidhi Independent PU College, Doddaballapur}{Aug 2020 -- Apr 2022}
      {Pre-University in PCMB - Percentage: 97.8\%}{}

    \resumeEduheading
      {Lavanya English High School, Doddaballapur}{Jul 2020}
      {Class 10 - Percentage: 95.36\%}{}
  \resumeSubHeadingListEnd

%-----------ADDITIONAL EXPERIENCE-----------------
\section{Additional Experiences}
  \resumeSubHeadingListStart
    \resumeItem{Intern - Rotary Bengaluru Reach Out: Supported community service project operations.}
    \resumeItem{Student Volunteer - Youth for Parivarthan: Contributed to Black Spot Fixing and Recyclothon initiatives.}
  \resumeSubHeadingListEnd

\end{document}
